It Is Unbearable To Breath Here': Air Quality, Open Incineration, And Misinformation In Blantyre, Malawi

### 2023-05-19 manuscript/manuscript.qmd
render

[^3]: Patients are required to bring a caregiver for in-patient
    hospitals stays, usually a family member, who assist with feeding,
    bathing, and all other non-medical services.

@@

Poor air quality in in African cities can be attributed to multiple
factors, including vehicular emissions, dust, or the use of low-quality
fuels for cooking, lighting, and heating, however, the open burning of
waste has been identified as one of the key contributors to air
pollution within urban areas [@amegah2018proliferation;
@bulto2020impact]. Although open trashing burning is a problem in LICs
broadly, for instance, @wiedinmyer2014global estimate that open trash
burning contributes to 29% of the total global PM~2.5~ anthropogenic
emissions, it is of particular concern in Sub-Saharan African (SSA)
cities, which are home to 19 of the world's 50 biggest dumpsites (United
Nations Development Programme, 2021). Particulate matter, or PM, is not
specific to trash burning, but rather the product of any type of
incomplete combustion and is one of the most commonly measured
indicators for air quality. PM is measured in terms of its particle size
and generally classified into PM with particle sizes less than 10 µm
(PM~10~) and those with sizes less than 2.5 µm (PM~2.5~), while one way
of measuring the severity of air pollution is by expressing the mass of
PM per volume of air (µg PMx/m^3^ air). PM has been linked to multiple
negative health outcomes. Amongst particulate air pollution, PM~10~ and
PM~2.5~ are of particular concern as they can penetrate deep into the
lungs, and their exposure has been associated with asthma, heart
disease, heart failure, stroke, and cancer [@mohapatra2014effect;
@xing2016impact]. As a result, the health impacts of ambient air
particle pollution may be significant, especially for the most
vulnerable. For instance, the @ihme2019ambient estimates PM related air
pollution resulted in 4.14 million deaths worldwide (in 2019), of which,
394,000 occurred in Africa. Yet, despite its importance, the air quality
and health picture in Africa is worryingly incomplete. For instance, the
WHO only collects data from 10 African countries (covering 39 cities)
[@worldhealthorganization2016ambient]. Likewise, robust, epidemiological
data from and for the African context is also lacking, though emerging
data suggests strong correlations between PM and poor health outcomes
[@coker2018narrative; @heft-neal2018robust]. Moving forward, it is not
just the air at Queen's which lacks clarity.

@@

-   When a patient arrives at QECH, she or he will usually arrive with a
    guardian: someone to cook for them, buy medicine, do their laundry,
    and help them bathe. The **Guardian Shelter** is a gender-separated
    concrete floor shelter for sleeping along with a cooking pavilion
    and toilet/shower block are maintained by a the local NGO Chira
    fund. Though simple, the facility is secure and offers one of the
    only free/accessible toilet facilities for visitors on the QECH
    campus.

@@

Despite its national prominence, and international reputation for
academic medical research, Queen's is plagued by constant shortages of
human and material resources. Yet, these shortages are not shared
equally across the space, with a sharp division in cleanliness,
resources, and quality of care between public wards, supported by the
Malawi Ministry of Health, and the private wads with international
funding, such as the aforementioned Mercy James Institute. For staff,
these shortages have manifested in poor salaries, missed pay cheques,
failing infrastructure and limited supplies [@kalina2020this]. Regarding
waste management, these shortages have manifested in a chronic shortage
of black bags, waste containers and cleaning staff. As a result, due to
a lack of bags and storage containers, there is minimal segregation of
waste, and highly infectious items (bandages, gloves, syringes, and
other sharps) are disposed of along with non-hazardous waste (food,
newspapers, packaging). As a result, rather than facilitating different
disposal pathways for hazardous and non-hazardous waste, all waste is
mixed, necessitating more burning than would be necessary if
non-hazardous waste was diverted, and contributing to workplace risk,
with reports of accidental exposure to potentially infected waste,
including accidental pokes from improperly disposed of sharps, common
amongst hospital staff. Regardless, separation ends at the point of
collection. The hospital is not serviced by regular municipal waste
collection, and as a result, nearly all of the waste produced by the
hospital, hazardous and non-hazardous, has to be disposed of on-site,
either within the limited capacity of the hospital incinerator, or more
commonly, through open burning. As a result, the constantly smouldering
pile of waste puts forth a continuous cloud of grey smoke, which
mingling with the dozens of other fires on the grounds, from cooking
fires and burning garden waste, blankets Queen's in a permanent cloud of
foul smelling haze.

@@

The PM monitoring device centres around a Raspberry Pi 3 Model B
single-board computer complete with an operating system and storage
space. The added advantage of storage space is that the data are not
lost if the internet connection breaks down. Because the Pi can only
read digital signals, we needed to include an analogue-to-digital (ADC)
converter. The amount of dust is measured by a Nova PM SDS011 High
Precision Laser sensor. This sensor measures particles at 2.5 and 10 µm
in diameter in mg/m^3^. A list of the specific hardware and software
components can be found in Appendix B.

@@

The choice of where the sensors were installed was done in collaboration
with the QECH administration, but the position of the sensors at the
individual buildings were decided by the research team. Four air quality
sensors were installed on the outside of buildings (Guardian Shelter,
Mercy James, Malaria Project, Lighthouse Clinic) while the remaining
four sensors were installed inside (Ward 6B, Administration, Lions
Sight, uMoyo). All of the sensors were mounted to a wall at a height of
approximately two metres from the ground with the help of QECH
maintenance department personnel. This height was chosen to prevent the
public from tampering with the equipment when they visit the hospital.
Additionally, we assured that each pipe that inhaled ambient air was
freely protruding in the building (room) in order to capture the air
quality.

@@

Knowing the exact burning locations and burning times, especially at the
incinerator and the Guardian Shelter, would have helped in better
identifying the sources and movements of the plumes. However, given the
size of the campus and it's 24-hour schedule, a much larger research
team would have been required to quantify all the burning. Finally, The
humidity, and the potential for interference was not accounted for; the
measurements were not adjusted for humidity which could affect the
values, though not enough to significantly alter the key findings and
need for immediate action.

@@

```{r}
#| label: tbl01-peaks
#| tbl-cap: Peaks for both PM~2.5~ and PM~10~ are the number of data points above the WHO interim target 1 (annual) which is the least stringent; the number of observations recorded (count) is provided for reference.

@@

Over the course of the two-month study, the hazardous limits for both
parameters were exceeded at all locations except for the Lions Sight
hospital. The limits were exceeded fewer than 50 times at five of the
locations, and only the monitors at the Lighthouse Clinic and the
Guardian Shelter recorded more than 50 instances above the hazardous
limits. At the Lighthouse Clinic, the PM~10~ limit was exceeded almost
twice as often as the PM~2.5~ limit, while at the Guardian Shelter, the
reverse is true. Because the Lighthouse Clinic is within 50 m of the
incinerator, the number and predominance of PM~10~ peaks is
characteristic of incomplete combustion and dust that is typical for the
area and the open burning that occurs there. The residents at the
Guardian Shelter however are mostly cooking within contained clay stoves
that have been designed to improve combustion of the coal and wood that
is burned within them. The fewer number of PM~10~ peaks is a testament
to this intervention, though the frequency of PM~2.5~ peaks is still
beyond acceptable.

@@

The 24-hour averaged values (logged every 5 minutes) are presented for
each location, for both PM~10~ and PM~2.5~ in fig-24-hour-average. As
well as dampening local variation and peaks, the WHO air quality
guidelines are also based on 24-hour averages which are the standard
against which the health risks can be judged.

@@

The daily averages at both the Lighthouse Clinic and the Guardian
Shelter are both consistently higher for both parameters and the two
averages closely followed the same general trends. Though the peaks at
the Lighthouse Clinic were higher than the Guardian Shelter, the low
values were consistently lower, indicating more times of little or no
burning, unlike the Guardian Shelter emissions which were relatively
constant. However, further analysis of 12 hour averages (8:00-15:59
(working hours) and 16:00-7:59 (evening)) did not indicate clear
differences between the time periods; stated differently, the data did
not clearly point to more or less burning in the day or at night.

```{r}
#| label: fig03-24-hour-average
#| fig-cap: Average 24-hour PM~10~ and PM~2.5~ at 8 monitoring stations over 2 months
#| fig-align: center

@@

```{r}
#| label: fig04-pm-ratios
#| fig-cap: PM~10~:PM~2.5~ values for each location. Each line shows the minimum and maximum ratio for the day based on ratios calculated hourly. Does not include 14th to 16th October at location uMoyo due to extreme outliers.
#| fig-align: center

@@

```{r}
#| label: fig05-percent-exposure
#| fig-cap: Percentage of measured values categorised according to WHO 2021 targets
#| fig-align: center
#| fig-height: 5

@@

Unsurprisingly, a majority of the air quality at the Lighthouse Clinic
and the Guardian Shelter falls at, or below, interim target 1. What is
less expected is that even though there are fewer days of hazardous or
very bad air quality at the other locations, most locations do not have
target 4 values for even half of the time. Mercy James, the Malaria
Project and Lions Sight have the largest percentages of days with air
quality meeting the interim target 4. Interim target 2 rated air
occupies an unexpectedly large proportion of the days at all locations,
indicating that although there are a few very toxic, and a few quite
good days, the majority of the air is actually neither, but still cause
for concern.

@@

Most staff, however, have been unable to find any way to mitigate the
impacts of the smoke, and only found relief once they reached home at
the end of their shift, as one of the janitorial staff described, "we
only feel safe when we are home". Of course, this relief is not
available for the hundreds of patients and caregivers who sleep at QECH
or are unable to leave. Ultimately, most place their hope in the
construction of the new incinerator (which had not yet been activated at
the time of the interviews), and biding their time as construction drags
on; coping as best they can. As the same member of the janitorial
staff[^11] described, "we are just hoping we will start breathing good
air soon, when the new incinerator is opened."

@@

The air quality, as a result of open waste burning at Queen's is poor
and not suitable for a city, let alone a hospital. Over the course of
this two-month study, the hazardous limits for both PM parameters were
exceeded at all locations except for the Lions Sight hospital. The WHO
limits were exceeded fewer than 50 times at five of the locations, and
only the monitors at the Lighthouse Clinic and the Guardian Shelter
recorded more than 50 instances above the most hazardous limit. The
composition of emissions recorded ranged significantly, analysed as the
ratio PM~10~:PM~2.5~ likely reflects a range of burning styles and/or
fuel (waste) type, and no discernible trend was observed.. Among
interview respondents, there was a general consensus that air quality
caused by the burning of waste within the hospital was a problem,
although there were significant differences between respondents over
their understandings of potential impacts, the effectiveness of various
coping mechanisms, and their problematisations linked to the burning of
specific waste materials. For most, going home or leaving the Queen's
campus was the only pathway to relief, though for patients who can not
leave, endurance was the only option. This work was originally planned
as a before-and-after study: we envisioned reporting these baseline
results compared to follow-up measurements once the long-promised
incinerator was commissioned. However, nearly 4 years later, the
incinerator is rarely functional (partly for technical reasons, partly
for financial ones) and the smoke hovering over Queen's is still thick.
Waste management has long been known as an environmental health issue,
but in the case of open trash burning at a medical facility, it becomes
more: for some of the most vulnerable, especially those with TB, asthma
or other chronic disease, it could be a matter of life or death.

@@

The authors are grateful to the staff, patients and caregivers at QECH
for their assistance, willingness to share their views, and importantly,
perseverance in delivering the best care possible under difficult
circumstances. Moreover, we would like to acknowledge the assistance and
effort of Open Data Durban, now the Open Cities Lab, for their
assistance in constructing and programming the sensors.

@@

```{r}
#| label: figA1-five-minute-intervals
#| fig-cap: PM~2.5~ and PM~10~ values collected every 5 minutes over 10 months at 8 locations.
#| fig-align: center

@@

1.  The Raspberry Pi operating system runs off of Rasbian software on a
    NOOBS scandisk.
2.  Air quality monitoring code is written in Python using the [aqi
    library](https://pypi.org/project/python-aqi/) (A library of
    algorithms to convert between AQI value and pollutant
    concentration). The code is stored on the [Open Data Durban GitHub
    account](https://github.com/opendatadurban/hospital_stations) and is
    free for all to access. To be able to collect data, the device needs
    to be connected to a reliable wifi network, the SSID and password
    need to be coded onto the device during step 2 in the building
    method.
3.  Once the whole device has been put together and placed on site, to
    access that data we use a combination of programs:

>>>>

[^3]: Patients are required to bring a caregiver for in-patient hospital
    stays, usually a family member, who assists with feeding, bathing,
    and all other non-medical services.

@@

Poor air quality in in African cities can be attributed to multiple
factors, including vehicular emissions, dust, or the use of low-quality
fuels for cooking, lighting, and heating, however, the open burning of
waste has been identified as one of the key contributors to air
pollution within urban areas [@amegah2018proliferation;
@bulto2020impact]. Although open trash burning is a problem in LICs
broadly, for instance, @wiedinmyer2014global estimate that open trash
burning contributes to 29% of the total global PM~2.5~ anthropogenic
emissions, it is of particular concern in Sub-Saharan African (SSA)
cities, which are home to 19 of the world's 50 biggest dumpsites (United
Nations Development Programme, 2021). Particulate matter, or PM, is not
specific to trash burning, but rather the product of any type of
incomplete combustion and is one of the most commonly measured
indicators for air quality. PM is measured in terms of its particle size
and generally classified into PM with particle sizes less than 10 µm
(PM~10~) and those with sizes less than 2.5 µm (PM~2.5~), while one way
of measuring the severity of air pollution is by expressing the mass of
PM per volume of air (µg PMx/m^3^ air). PM has been linked to multiple
negative health outcomes. Amongst particulate air pollution, PM~10~ and
PM~2.5~ are of particular concern as they can penetrate deep into the
lungs, and their exposure has been associated with asthma, heart
disease, heart failure, stroke, and cancer [@mohapatra2014effect;
@xing2016impact]. As a result, the health impacts of ambient air
particle pollution may be significant, especially for the most
vulnerable. For instance, the @ihme2019ambient estimates PM related air
pollution resulted in 4.14 million deaths worldwide (in 2019), of which,
394,000 occurred in Africa. Yet, despite its importance, the air quality
and health picture in Africa is worryingly incomplete. For instance, the
WHO only collects data from 10 African countries (covering 39 cities)
[@worldhealthorganization2016ambient]. Likewise, robust, epidemiological
data from and for the African context is also lacking, though emerging
data suggests strong correlations between PM and poor health outcomes
[@coker2018narrative; @heft-neal2018robust]. Moving forward, it is not
just the air at Queen's which lacks clarity.

@@

-   When a patient arrives at QECH, she or he will usually arrive with a
    guardian: someone to cook for them, buy medicine, do their laundry,
    and help them bathe. The **Guardian Shelter** is a gender-separated
    concrete floor shelter for sleeping along with a cooking pavilion
    and toilet/shower block that are maintained by a local NGO, Chira
    fund. Though simple, the facility is secure and offers one of the
    only free/accessible toilet facilities for visitors on the QECH
    campus.

@@

Despite its national prominence, and international reputation for
academic medical research, Queen's is plagued by constant shortages of
human and material resources. Yet, these shortages are not shared
equally across the space, with a sharp division in cleanliness,
resources, and quality of care between public wards, supported by the
Malawi Ministry of Health, and the private wads with international
funding, such as the aforementioned Mercy James Institute. For staff,
these shortages have manifested in poor salaries, missed pay cheques,
failing infrastructure and limited supplies [@tilley2020wea]. Regarding
waste management, these shortages have manifested in a chronic shortage
of black bags, waste containers and cleaning staff. As a result, due to
a lack of bags and storage containers, there is minimal segregation of
waste, and highly infectious items (bandages, gloves, syringes, and
other sharps) are disposed of along with non-hazardous waste (food,
newspapers, packaging). As a result, rather than facilitating different
disposal pathways for hazardous and non-hazardous waste, all waste is
mixed, necessitating more burning than would be necessary if
non-hazardous waste was diverted, and contributing to workplace risk,
with reports of accidental exposure to potentially infected waste,
including accidental pokes from improperly disposed of sharps, common
amongst hospital staff [@kalina2020this]. Regardless, separation ends at
the point of collection. The hospital is not serviced by regular
municipal waste collection, and as a result, nearly all of the waste
produced by the hospital, hazardous and non-hazardous, has to be
disposed of on-site, either within the limited capacity of the hospital
incinerator, or more commonly, through open burning. As a result, the
constantly smouldering pile of waste puts forth a continuous cloud of
grey smoke, which mingling with the dozens of other fires on the
grounds, from cooking fires and burning garden waste, blankets Queen's
in a permanent cloud of foul smelling haze.

@@

The PM monitoring device centres around a Raspberry Pi 3 Model B
single-board computer complete with an operating system and storage
space. The added advantage of storage space is that the data are not
lost if the internet connection breaks down. Because the Pi can only
read digital signals, we needed to include an analogue-to-digital (ADC)
converter. The amount of dust is measured by a Nova PM SDS011 High
Precision Laser sensor. This sensor measures particles at 2.5 and 10 µm
in diameter in µg/m^3^. A list of the specific hardware and software
components can be found in Appendix B.

@@

The choice of where the sensors were installed was done in collaboration
with the QECH administration, but the position of the sensors at the
individual buildings were decided by the research team. Four air quality
sensors were installed on the outside of buildings (Guardian Shelter,
Mercy James, Malaria Project, Lighthouse Clinic) while the remaining
four sensors were installed inside (Ward 6B, Administration, Lions
Sight, uMoyo). All of the sensors were mounted to a wall at a height of
approximately two metres from the ground with the help of QECH
maintenance department personnel. TThis height was chosen to both
capture the approximate breathing zone and to prevent the public from
tampering with the equipment when they visit the hospital. Additionally,
we assured that each pipe that inhaled ambient air was freely protruding
in the building (room) in order to capture the airquality.

@@

Knowing the exact burning locations and burning times, especially at the
incinerator and the cooking times at the Guardian Shelter (though it is
nearly constant), would have helped in better identifying the sources
and movements of the plumes. However, given the size of the campus and
its 24-hour schedule, a much larger research team would have been
required to quantify all the burning. Finally, the relative humidity,
and the potential for interference was not accounted for; the
measurements were not adjusted for humidity which could affect the
values, though not enough to significantly alter the key findings and
need for immediate action.

@@

```{r}
#| label: tbl-peaks
#| tbl-cap: Peaks for both PM~2.5~ and PM~10~ are the number of data points above the WHO interim target 1 (annual) which is the least stringent; the number of observations recorded (count) is provided for reference.

@@

Over the course of the two-month study, the hazardous limits for both
parameters were exceeded at all locations except for the Lions Sight
hospital. The limits were exceeded fewer than 50 times at five of the
locations, and only the monitors at the Lighthouse Clinic and the
Guardian Shelter recorded more than 50 instances above the hazardous
limits. At the Lighthouse Clinic, the PM~10~ limit was exceeded almost
twice as often as the PM~2.5~ limit, while at the Guardian Shelter, the
reverse is true. Because the Lighthouse Clinic is within 50 m of the
incinerator, the number and predominance of PM~10~ peaks is
characteristic of incomplete combustion and dust that is typical for the
area and the open burning that occurs there. Although there is trash
burning at the Guardian Shelter, the main source of smoke is from the
constant cooking. The residents at the Guardian Shelter are mostly
cooking coal and wood that is burned within small "improved" cooking
stoves that are contained, in a row, within a dedicated cooking block.
The fewer number of PM10 peaks is a testament to this intervention,
though the frequency of PM2.5 peaks is still beyond acceptable.

@@

The 24-hour averaged values (logged every 5 minutes) are presented for
each location, for both PM~10~ and PM~2.5~ in @fig-24-hour-average. As
well as dampening local variation and peaks, the WHO air quality
guidelines are also based on 24-hour averages which are the standard
against which the health risks can be judged.

@@

The daily averages at both the Lighthouse Clinic and the Guardian
Shelter are both consistently higher for both parameters and the two
averages closely follow the same general trends. Though the peaks at the
Lighthouse Clinic were higher than the Guardian Shelter, the low values
were consistently lower, indicating more times of little or no burning,
unlike the Guardian Shelter emissions which were relatively constant.
However, further analysis of 12 hour averages (8:00-15:59 (working
hours) and 16:00-7:59 (evening)) did not indicate clear differences
between the time periods; stated differently, the data did not clearly
point to more or less burning in the day or at night.

```{r}
#| label: fig-24-hour-average
#| fig-cap: Average 24-hour PM~10~ and PM~2.5~ at 8 monitoring stations over 2 months
#| fig-align: center

@@

```{r}
#| label: fig-pm-ratios
#| fig-cap: PM~10~:PM~2.5~ values for each location. Each line shows the minimum and maximum ratio for the day based on ratios calculated hourly. Does not include 14th to 16th October at location uMoyo due to extreme outliers.
#| fig-align: center

@@

```{r}
#| label: fig-percent-exposure
#| fig-cap: Percentage of measured values categorised according to WHO 2021 targets
#| fig-align: center
#| fig-height: 5

@@

Unsurprisingly, a majority of the air quality at the Lighthouse Clinic
and the Guardian Shelter falls at, or above, interim target 1. What is
less expected is that even though there are fewer days of hazardous or
very bad air quality at the other locations, most locations do not have
target 4 values for even half of the time. Mercy James, the Malaria
Project and Lions Sight have the largest percentages of days with air
quality meeting the interim target 4, which is expected as these
locations are further away from the main burning site. Interim target 2
rated air occupies an unexpectedly large proportion of the days at all
locations, indicating that although there are a few very toxic, and a
few quite good days, the majority of the air is actually neither, but
still cause for concern.

@@

Most staff, however, have been unable to find any way to mitigate the
impacts of the smoke, and only found relief once they reached home at
the end of their shift, as one of the janitorial staff described, "we
only feel safe when we are home". Of course, this relief is not
available for the hundreds of patients and caregivers who sleep at QECH
or are unable to leave. Ultimately, most place their hope in the
construction of the new incinerator (which had not yet been activated at
the time of the interviews), and biding their time as construction drags
on; coping as best they can. As the same member of the janitorial
staff[^12] described, "we are just hoping we will start breathing good
air soon, when the new incinerator is opened."

[^12]: ID14, 2019-11-23

@@

The air quality, as a result of open waste burning at Queen's is poor
and not suitable for a city, let alone a hospital. Over the course of
this two-month study, the hazardous limits for both PM parameters were
exceeded at all locations except for the Lions Sight hospital. The WHO
limits were exceeded fewer than 50 times at five of the locations, and
only the monitors at the Lighthouse Clinic and the Guardian Shelter
recorded more than 50 instances above the most hazardous limit. The
results for the Lighthouse Clinic are directly related to the main trash
burning site, while the worrisome air quality at the Guardian Shelter is
primarily from near constant cooking with coal. Simple improvements to
the cooking block (e.g. Whirlybird vents) could at least vent the smoke
above the roof and improve the air quality at human level. The
composition of emissions recorded ranged significantly, analysed as the
ratio PM~10~:PM~2.5~ likely reflects a range of burning styles and/or
fuel (waste) type, and no discernible trend was observed. Among
interview respondents, there was a general consensus that air quality
caused by the burning of waste within the hospital was a problem,
although there were significant differences between respondents over
their understandings of potential impacts, the effectiveness of various
coping mechanisms, and their problematisations linked to the burning of
specific waste materials. For most, going home or leaving the Queen's
campus was the only pathway to relief, though for patients who can not
leave, endurance was the only option. This work was originally planned
as a before-and-after study: we envisioned reporting these baseline
results compared to follow-up measurements once the long-promised
incinerator was commissioned. However, nearly 4 years later, the
incinerator is rarely functional (partly for technical reasons, partly
for financial ones) and the smoke hovering over Queen's is still thick.
Waste management has long been known as an environmental health issue,
but in the case of open trash burning at a medical facility, it becomes
more: for some of the most vulnerable, especially those with TB, asthma
or other chronic disease, it could be a matter of life or death.

@@

The authors are grateful to the staff, patients and caregivers at QECH
for their assistance, willingness to share their views, and importantly,
perseverance in delivering the best care possible under difficult
circumstances. Moreover, we would like to acknowledge the assistance and
effort of the Open Cities Lab (formerly Open Data Durban), for their
assistance in constructing and programming the sensors.

@@

```{r}
#| label: fig-five-minute-intervals
#| fig-cap: PM~2.5~ and PM~10~ values collected every 5 minutes over 10 months at 8 locations.
#| fig-align: center

@@

1.  The Raspberry Pi operating system runs off of Rasbian software on a
    NOOBS scandisk.
2.  Air quality monitoring code is written in Python using the [aqi
    library](https://pypi.org/project/python-aqi/) (A library of
    algorithms to convert between AQI value and pollutant
    concentration). To be able to collect data, the device needs to be
    connected to a reliable wifi network, the SSID and password need to
    be coded onto the device during step 2 in the building method.
3.  Once the whole device has been put together and placed on site, to
    access that data we use a combination of programs:
